### 2019-10-01 proglog.tex

\subsubsection{Technical Tours}
Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors. Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.

The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. 
\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Petascale Computing Facility (NPCF) - Blue Waters}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

@@

\noindent{
\begin{minipage}{0.5\textwidth}
\textbf{Argonne National Laboratory}\\
Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale. With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science. Argonne is two-and-a-half-hour drive away. Bus transportation will be provided. On the tour, students will be guided around the site’s scientific and engineering facilities.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{argonne.png}
	\captionof{figure}{Argonne National Laboratory}
\end{minipage}}

\noindent{
\begin{minipage}{0.5\textwidth}
	\includegraphics[width=\textwidth]{clintonpp.jpg}
	\captionof{figure}{Clinton Powerplant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}}

@@

\vspace{0.5cm}
\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{NPRE Lab Tours}\\
Attendees will be able to take a tour of the various NPRE labs on campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA. There are also many other historical artifacts on display for participants to see. This tour will depart from the front entrance of the Illini Union.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.75\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\

>>>>

\subsubsection{Technical Tours}
Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors. Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.\\

The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. \\

\noindent{
\begin{minipage}{0.5\textwidth}
	\textbf{National Petascale Computing Facility (NPCF) - Blue Waters}\\
Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world. The NCSA is within walking distance from all conference hotels. During the tour, attendees will tour the machine room and witness some of the beautiful results it produces. Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{bw_front.png}
	\captionof{figure}{Blue Waters Supercomputer}
\end{minipage}
}

@@

\noindent{
\begin{minipage}{0.5\textwidth}
\textbf{Argonne National Laboratory}\\
Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale. With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science. Argonne is two-and-a-half-hour drive away. Bus transportation will be provided. On the tour, students will be guided around the site’s scientific and engineering facilities.
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{argonne.png}
	\captionof{figure}{Argonne National Laboratory}
\end{minipage}}

\vspace{0.5cm}
\noindent{
\begin{minipage}{0.5\textwidth}
	\centering
	\includegraphics[width=0.9\textwidth]{clintonpp.jpg}
	\captionof{figure}{Clinton Powerplant on Clinton Lake}
\end{minipage}
\begin{minipage}{0.5\textwidth}
	\textbf{Clinton Nuclear Power Plant}\\
Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987. They currently serve over one million customers and operate 94.9$\%$ of the time. The tour will be held on Thursday morning and bus transportation will be provided. Attendees will be guided by a Clinton employee. The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
\end{minipage}}

@@

\vspace{0.5cm}
\noindent{\begin{minipage}{0.5\textwidth}
	\textbf{NPRE Lab Tours}\\
Attendees will be able to take a tour of the various NPRE labs on campus. They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located. Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods. After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA. There are also many other historical artifacts on display for participants to see. This tour will depart from the front entrance of the Illini Union.
\end{minipage}
\hspace{0.5cm}
\begin{minipage}{0.45\textwidth}
	\centering
	\includegraphics[width=0.85\textwidth]{creek.png}
	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
\end{minipage}}
\\

### 2019-10-01 socials.tex

	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{77club1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{77club2.png}
	\end{subfigure}
	\caption{77 Club at Memorial Stadium}		
\end{figure}

\subsubsection{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel. This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities. This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
\vspace{0.5cm}\newline
% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}

\subsubsection{Bars in the Downtown Champaign District} 
The downtown Champaign area on the north-east block of University Ave. and Neil St. offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than attend the Illini Union Rec Room. Reservations will be made in advance and several bars can accompany up to 100 patrons or more in the area. Some of the recommended bars that the conference planning committee recommend that would be great sponsorship opportunities are Pour Bros. Taproom (up to 100 guest reservation), Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits). Conveniently, the recommended bars are just a couple of blocks from each other, and transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
\vspace{0.5cm}\newline
% Pour Bros Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
	\end{subfigure}	
	\caption{Pour Brothers Taproom}	
\end{figure}

% Guido's and Barrelhouse Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{guidos.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{barrelhouse.png}
	\end{subfigure}	
	\caption{Guido's (left) and Barrelhouse (right)}	
\end{figure}

@@

%\subsubsection{Under 21 Social: University of Illinois Ice Arena}
%For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.
%\vspace{0.5cm}\newline
%% Ice Arena Picture
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.8\textwidth]{ice_arena.png}
%	\caption{The UIUC Ice Arena}
%\end{figure}

>>>>

	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.6\linewidth]{77club1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.75\linewidth]{77club2.png}
	\end{subfigure}
	\caption{77 Club at Memorial Stadium}		
\end{figure}

% \subsubsection{Illini Union Rec Room Lockout}
% The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel. This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities. This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
% \vspace{0.5cm}\newline
% % Illini Union Rec Room Picture
% \begin{figure}[H]
% 	\centering
% 	\begin{subfigure}{0.5\textwidth}
% 		\centering
% 		\includegraphics[width=0.75\linewidth]{union_recroom1.png}
% 	\end{subfigure}%
% 	\begin{subfigure}{0.5\textwidth}
% 		\centering
% 		\includegraphics[width=0.75\linewidth]{union_recroom2.png}
% 	\end{subfigure}	
% 	\caption{Illini Union Rec Room}	
% \end{figure}

\subsubsection{Bars in the Downtown Champaign District} 
The downtown Champaign area on the north-east block of University Ave. and Neil St. offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than go Ice Skating at the Ice Arena. Reservations will be made in advance and several bars can accompany up to 100 patrons or more in the area. A couple of bars that the conference planning committee recommends are Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits). Conveniently, these bars are just a couple of blocks from each other with several more in between. Transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
\vspace{0.5cm}\newline
% % Pour Bros Picture
% \begin{figure}[H]
% 	\centering
% 	\begin{subfigure}{0.5\textwidth}
% 		\centering
% 		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
% 	\end{subfigure}%
% 	\begin{subfigure}{0.5\textwidth}
% 		\centering
% 		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
% 	\end{subfigure}	
% 	\caption{Pour Brothers Taproom}	
% \end{figure}

% Guido's and Barrelhouse Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.65\linewidth]{guidos.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.65\linewidth]{barrelhouse.png}
	\end{subfigure}	
	\caption{Guido's (left) and Barrelhouse (right)}	
\end{figure}

@@

\subsubsection{Under 21 Social: University of Illinois Ice Arena}
For students under the drinking age that cannot attend the Champaign Bars social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst. Snacks and concession items are also available.
\vspace{0.5cm}\newline
% Ice Arena Picture
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ice_arena.png}
	\caption{The UIUC Ice Arena}
\end{figure}
